|

### 2025-07-10 output/IMPS-2025-slideshow.qmd
Update content styles to fit slides better

:::::: {.fragment fragment-index="1"}
::: r-stack
[$a_1$ = 1.0; $b_1$ = 0.0]{style="color:#5c6eb1;"}
:::

::: r-stack
[$a_2$ = 1.0; $b_2$ = 1.5]{style="color:#90214a;"}
:::

::: r-stack
[$a_3$ = 2.5; $b_3$ = 0.0]{style="color:#749f4c;"}
:::
::::::
:::::::

@@

-   Increasing monotony:

@@

---(p. 402)

-   Orthogonality

@@

---(p. 404)

@@

## Assumptions: Increasing monotony

@@

## Assumptions: Increasing monotony {.smaller}

@@

> "*I neglect my duties*"

-- [International Personality Item Pool](https://ipip.ori.org/newAB5CKey.htm#Conscientiousness)

:::::: {.columns .fragment}
::: {.column .r-center}
```{r inverse-item-curve}
#| fig-align:  center
#| fig-asp:    0.5344
#| fig-width:  9

@@

logit_curve_data_long |>
  ggplot(
    mapping = aes(
      latent_trait, prob,
      color = item,
      group = after_scale(color)
    )
  )                                                        +
  geom_line(linewidth = LINE_WIDTH)                        +
  labs(x = "Conscientiousness", y = "P(Y~i~ = 1)")           +
  scale_y_continuous(
    breaks       = 0:1,
    minor_breaks = NULL,
    limits       = 0:1,
    expand       = expansion(mult = c(0, .05))
  )                                                        +
  scale_x_continuous(
    minor_breaks = NULL,
    expand = expansion()
  )                                                        +
  scale_color_manual(values = ITEMS_PALETTE, guide = NULL) +
  theme(
    axis.title       = element_markdown(),
    axis.title.x     = element_text(margin = margin(t = 1, unit = "lines")),
    axis.title.y     = element_markdown(angle = 90),
    panel.grid.major = element_line(linetype = "17", linewidth = GRID_WIDTH),
    # The following is necessary to avoid showing the axis breaks, as dropping
    #   them prevents the axis line from being drawn (see
    #   https://github.com/tidyverse/ggplot2/issues/2983)
    axis.text.x.bottom = element_blank(),
    axis.ticks.length.x.bottom = unit(0, units = "cm"),
    panel.grid.major.x = element_blank()
  )
```
:::

:::: {.column .r-center}
$$
  P(Y_i = 1) = \Phi_L (a_i (\theta - b_i))
$$

::: r-stack
[$a_i < 0$]{style="color:#5c6eb1;"}
:::
::::
::::::

>>>>

:::::: {.fragment fragment-index="1"}
::: {.r-stack style="color:#5c6eb1;"}
$a_1$ = 1.0; $b_1$ = 0.0
:::

::: {.r-stack style="color:#90214a;"}
$a_2$ = 1.0; $b_2$ = 1.5
:::

::: {.r-stack style="color:#749f4c;"}
$a_3$ = 2.5; $b_3$ = 0.0
:::
::::::
:::::::

@@

-   Increasing monotony (p. 402):

@@

-   Orthogonality (p. 404):

@@

@@

## Increasing monotony

@@

## Increasing monotony {.smaller}

@@

::::: columns
::: column
> "*I neglect my duties*"

-- [International Personality Item Pool](https://ipip.ori.org/newAB5CKey.htm#Conscientiousness)
:::

::: {.column .fragment fragment-index="1"}
```{r inverse-item-curve}
#| fig-align:  center
#| fig-asp:    0.5344
#| fig-width:  9

@@

logit_curve_data_long |>
  ggplot(
    mapping = aes(
      latent_trait, prob,
      color = item,
      group = after_scale(color)
    )
  )                                                        +
  geom_line(linewidth = LINE_WIDTH)                        +
  labs(x = "Conscientiousness", y = "P(Y~i~ = 1)")           +
  scale_y_continuous(
    breaks       = 0:1,
    minor_breaks = NULL,
    limits       = 0:1,
    expand       = expansion(mult = c(0, .05))
  )                                                        +
  scale_x_continuous(
    minor_breaks = NULL,
    expand = expansion()
  )                                                        +
  scale_color_manual(values = ITEMS_PALETTE, guide = NULL) +
  theme(
    axis.title       = element_markdown(),
    axis.title.x     = element_text(margin = margin(t = 1, unit = "lines")),
    axis.title.y     = element_markdown(angle = 90),
    panel.grid.major = element_line(linetype = "17", linewidth = GRID_WIDTH),
    # The following is necessary to avoid showing the axis breaks, as dropping
    #   them prevents the axis line from being drawn (see
    #   https://github.com/tidyverse/ggplot2/issues/2983)
    axis.text.x.bottom = element_blank(),
    axis.ticks.length.x.bottom = unit(0, units = "cm"),
    panel.grid.major.x = element_blank()
  )
```
:::
:::::

::::: {.columns .fragment fragment-index="1"}
::: column
$$
  P(Y_i = 1) = \Phi_L (a_i (\theta - b_i))
$$
:::

::: {.column style="color:#5c6eb1;"}
$$
  a_i < 0
$$
:::
:::::
